Talks

### 2025-06-03 talks.qmd
update

- June 4. Evolution and Social Cognition lab,	Institut Jean Nicod, Paris.

>>>>

- June 4. ["Do we truly understand those we disagree with, and how could we test this?
The Ideological Turing test"](https://docs.google.com/presentation/d/19QBDb20G9QWzebz7sgbxi80xDxisy_LDCaQGvHIcQxU/edit?usp=sharing), Evolution and Social Cognition lab,	Institut Jean Nicod, Paris.
